### 2016-09-30 architecture.tex
"fine-grained"
I think these should be two sentences (previous wording did not make sense)

For this reason, a new project called SymEngine~\cite{SymEngine} has been started.
The aim of this poject is to develop a library with better performance
characteristics for symbolic manipulation. SymEngine is a pure C++ library,
which allows it fine grain control over the memory layout of expressions.
SymEngine has thin wrappers to other languages (Python, Ruby,
Julia, etc.) whose aim is to be the fastest symbolic manipulation library. Preliminary
benchmarks suggest that SymEngine is as performant as its commercial and
open source competitors.

>>>>

For this reason, a new project called SymEngine~\cite{SymEngine} has been started.
The aim of this poject is to develop a library with better performance
characteristics for symbolic manipulation. SymEngine is a pure C++ library,
which allows it fine-grained control over the memory layout of expressions.
SymEngine has thin wrappers to other languages (Python, Ruby,
Julia, etc.). Its aim is to be the fastest symbolic manipulation library. Preliminary
benchmarks suggest that SymEngine is as performant as its commercial and
open source competitors.
